Human Factors Influencing Visual Statistical Inference

### 2017-10-17 sociology_paper.Rnw
updated section 4.1

\subsection{Overview of the Data} A total of 2321 participants provided feedback data on the lineups in ten different experimental studies. Figure~\ref{fig:turker_location} displays the locations of participants around the world.  Most of the participants were from the United States and India. There were 76 other different countries represented. This provides a diverse pool of participants. The diversity in not only  geographic but also in gender, age group and education level as can be seen in Table~\ref{tbl:demographics}. % It is interesting that there were large number of female participants even though there were a lot of participants  from developing countries.
The large number of female participants from all countries was a pleasant surprise to us.

@@

Besides the United States and India, countries such as Canada, Romania, the United Kingdom and Macedonia have more than 10 participants each. The remaining 70 countries have fewer than 10 participants each. The distribution of participants is similar in all ten experiments. %This may be due to the time of day when the experiment was made available. %For some experiments more people participated from India than the United States and for others numbers were reversed (Figure~\ref{fig:participation_time}). It is also observed in some experiments that number of  participants are similar no matter whether the experiment is run on day time or nigh time. (*** Took out reference to Figure~11 in appendix.)

@@

In terms of academic background, the majority of participants had a graduate degree (a total of 902 participants, about 38.51\%). Examining the participants' location in conjunction with the academic background reveals that there is an above average  number of participants from India reporting to have a graduate degree. In retrospect this turned out to be a culturally based misunderstanding, as any university degree in India is considered to be a graduate degree, while the North American definition of a graduate degree refers to a Masters level education or above. Most of the  participants from the U.S. report to have an undergraduate degree or at least have some undergraduate courses.

@@

A total of 1911 lineups were evaluated in the ten experiments. Each person evaluated at least 10 lineups except for experiment~9 where each participant evaulated three lineups.
As a measure to ensure a high quality in the evaluations,
 a test plot was shown to each observer, and the performance on this test plot was used for screening purposes. %A test plot was shown to each observer and the feedback received from that plot is used to ensure data quality. 
Test plots were chosen in a way that any serious attempt at answering the lineup would result in a correct answer.
Data from participants who gave the wrong answer on the test plot % were considered as gaming the system, and their data were removed.
led to the removal of all of their answers from the analysis. 
Results from test plots were also not considered in any of the analyses.
 In some cases  participants chose to not provide their demographic information. Also, for some ip address, the actual geographical locations could not be retrieved. This resulted in some missing demographic information.

>>>>

\subsection{Overview of the Data} A total of 2340 participants provided feedback data on the lineups in ten different experimental studies. Figure~\ref{fig:turker_location} displays the locations of participants around the world.  Most of the participants were from the United States and India. There were 70 other different countries represented. This provides a diverse pool of participants. The diversity in not only  geographic but also in gender, age group and education level as can be seen in Table~\ref{tbl:demographics}. % It is interesting that there were large number of female participants even though there were a lot of participants  from developing countries.
The large number of female participants from all countries was a pleasant surprise to us.

@@

Besides the United States and India, countries such as Canada, Romania, the United Kingdom and Macedonia have more than 10 participants each. The remaining 64 countries have fewer than 10 participants each. The distribution of participants is similar in all ten experiments. %This may be due to the time of day when the experiment was made available. %For some experiments more people participated from India than the United States and for others numbers were reversed (Figure~\ref{fig:participation_time}). It is also observed in some experiments that number of  participants are similar no matter whether the experiment is run on day time or nigh time. (*** Took out reference to Figure~11 in appendix.)

@@

In terms of academic background, the majority of participants had a graduate degree (a total of 899 participants, about 38.42\%). Examining the participants' location in conjunction with the academic background reveals that there is an above average  number of participants from India reporting to have a graduate degree. In retrospect this turned out to be a culturally based misunderstanding, as any university degree in India is considered to be a graduate degree, while the North American definition of a graduate degree refers to a Masters level education or above. Most of the  participants from the U.S. report to have an undergraduate degree or at least have some undergraduate courses.

@@

A total of 1912 lineups were evaluated in the ten experiments. Each person evaluated at least 10 lineups except for experiment~9 where each participant evaulated three lineups.
As a measure to ensure a high quality in the evaluations,
 a test plot was shown to each observer, and the performance on this test plot was used for screening purposes. %A test plot was shown to each observer and the feedback received from that plot is used to ensure data quality. 
Test plots were chosen in a way that any serious attempt at answering the lineup would result in a correct answer.
Data from participants who gave the wrong answer on the test plot % were considered as gaming the system, and their data were removed.
led to the removal of all of their answers from the analysis. 
Results from test plots were also not considered in any of the analyses.
 In some cases  participants chose to not provide their demographic information. Also, for some ip address, the actual geographical locations could not be retrieved. This resulted in some missing geographic information.
